IIIDYT at IEST 2018: Implicit Emotion Classification With Deep Contextualized Word Representations

### 2018-08-28 paper/paper.tex
Update some captions and figures in paper

\documentclass[11pt,a4paper]{article}
\pdfoutput=1
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{images/best_ensembles.eps}
\caption{Best Macro F1 vs. Number of Ensembled Models.}
\label{fig:best_ensembles}
\end{figure}

@@

    \end{tabular}
    \caption{Ablation study results.}
    \label{table:ablation}

@@

Accuracies were obtained from the
validation dataset. Each model was trained with the same random seed and hyperparameters, save for the one listed. ``No emoji'' is the same model trained on the training dataset with no emoji, ``No ELMo'' corresponds to having switched the ELMo word encoding layer with a simple pre-trained GloVe embedding lookup, and ``Concat Pooling'' obtained sentence representations by using the pooling method described by \citet{howard2018universal}. ``LSTM hidden'' corresponds to the the hidden dimension of the BiLSTM, ``POS emb dim'' to the dimension of the part-of-speech embeddings, and ``SGD optim lr'' to the learning rate used while optimizing with the schedule described by \citet{conneau2017supervised}.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{images/dropout_table.pdf}
\caption{Dropout Variations. Rows correspond to the dropout applied both after the ELMo layer (word encoding layer) and after the fully-connected network's hidden layer, while columns correspond to the dropout applied after the max-pooling operation (sentence encoding layer.}
\label{fig:dropouts}
\end{figure}

@@

    \caption{Fine grained performance on tweets containing emoji, and the effect of removing them. \textbf{N} is the total number of tweets containing the listed emoji, \textbf{\#} and \textbf{\%} the number and percentage of correctly-classified tweets respectively, and $\bf{\Delta}$\textbf{\%} the variation of test accuracy when removing the emoji from the tweets.}

>>>>

\documentclass[11pt,a4paper]{article}
\pdfoutput=1
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{caption}
\usepackage{blindtext}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{images/best_ensembles.eps}
\caption{Effect of the number of ensembled models on validation performance.}
\label{fig:best_ensembles}
\end{figure}

@@

    \caption{Ablation study results.}
    \vspace{-0.4cm}
    \caption*{
        \footnotesize Accuracies were obtained from the
        validation dataset. Each model was trained with the same random seed and
        hyperparameters, save for the one listed. ``No emoji'' is the same model
        trained on the training dataset with no emoji, ``No ELMo'' corresponds
        to having switched the ELMo word encoding layer with a simple
        pre-trained GloVe embedding lookup table, and ``Concat Pooling''
        obtained sentence representations by using the pooling method described
        by \citet{howard2018universal}. ``LSTM hidden'' corresponds to the the
        hidden dimension of the BiLSTM, ``POS emb dim'' to the dimension of the
        part-of-speech embeddings, and ``SGD optim lr'' to the learning rate
        used while optimizing with the schedule described by \citet{conneau2017supervised}.}

    \label{table:ablation}

@@

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{images/dropout_table.pdf}

    \caption{Dropout Ablation. }
    \vspace{-0.4cm}

    \caption*{
        \footnotesize Rows correspond to the dropout applied both after
        the ELMo layer (word encoding layer) and after the fully-connected network's
        hidden layer, while columns correspond to the dropout applied after the
        max-pooling operation (sentence encoding layer.)}

\label{fig:dropouts}
\end{figure}

@@

    \caption{Fine grained performance on tweets containing emoji, and the effect
of removing them.} 
    \vspace{-0.4cm}
    \caption*{
        \footnotesize \textbf{N} is the total number of tweets containing the listed emoji,
        \textbf{\#} and \textbf{\%} the number and percentage of correctly-classified
        tweets respectively, and $\bf{\Delta}$\textbf{\%} the variation of test accuracy
        when removing the emoji from the tweets.}
